The benefits of an extended feature space in a machine learning bot for the game Schnapsen

### 2018-02-01 Text/paper.tex
added table + and -, and started with findings

\usepackage{listings}
\usepackage{enumerate}
\usepackage{graphicx} % Required for including images
\usepackage[font=small,labelfont=bf]{caption}

@@

\begin{center}
  \begin{tabular}{ | l | l l | l l | l l | | l l | }
     \hline
      & \textbf{rand} & & \textbf{bully} & & \textbf{rdeep} & & \textbf{Total} & \\
      & wins & losses & wins & losses & wins & losses  & wins & losses\\ \hline
      ml\_minimal & 843 & 237 & 837 & 243 & 348 & 732 & 2028 & 1212 \\ \hline
      ml\_stripped & 736 & 344 & 843 & 237 & 283 & 797 & 1862 & 1378  \\ \hline
      ml & 866 & 214 & 876 & 204 & 257 & 823 & 1999 & 1241 \\ \hline
      ml\_enriched & 881 & 119 & 797 & 283 & 284 & 798 & 1962 & 1278 \\ \hline
      ml\_advanced  & 856 & 224 & 808 & 272 & 292 & 788 & 1956 & 1284 \\ \hline
      ml\_combined & 949 & 131 & 759 & 321 & 274 & 806 & 1982 & 1258 \\ \hline
  \end{tabular}
\end{center}

\textbf{Table 1}: Overview of tournament wins and losses per ml-bot. \\

\begin{center}
\begin{tabular}{| r | r | r | r || r |}
\hline
      & \textbf{rand} & \textbf{bully} & \textbf{rdeep} & \textbf{Total} \\ \hline
      ml\_minimal & -2,65\% & -4,45\% & +35,4\% & \textbf{+1,45\%}   \\ \hline
      ml\_stripped & -15\% & -3,76\% & 10,11\% & \textbf{-6,85\%}  \\ \hline
      ml\_enriched & +1,73\% & -9,01\% & 10,5\% & \textbf{- 1,85\%} \\ \hline
      ml\_advanced & -1,15\% & -7,76\% & 13,6\%& \textbf{-2,15\%}  \\ \hline
      ml\_combined & 9,58\% & -13,35\% & 6,61\% & \textbf{-0,85\%}  \\ \hline \hline
      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{15,24\%} & \textbf{-2,05\%} \\ \hline
\end{tabular} \\
\end{center}

@@

\begin{center}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotRand.png}
\captionof{figure}{Part of games won against Rand}
\end{minipage}
\hfill
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotBully.png}
\captionof{figure}{Part of games won against Bully}
\end{minipage}
      \\ %extra line for space
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\linewidth]{images/barplotRdeep.png}
\captionof{figure}{Part of games won against Rdeep (notice the Y-axis)}
\end{minipage}
\end{center}

The collected data .............

\section{Findings}

>>>>

\usepackage{listings}
\usepackage{enumerate}
\usepackage{graphicx} % Required for including images
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}

@@

\setlength{\leftmargin}{0pt}
\begin{center}
  \begin{tabular}{ | l | l l | l l | l l | |l l | }
     \hline
      & \textbf{rand} & & \textbf{bully} & & \textbf{rdeep} & & \textbf{Total} & \\
      & wins & losses & wins & losses & wins & losses  & wins & losses \\ \hline
      ml\_minimal & 843 & 237 & 837 & 243 & 348 & 732 & 2028 & 1212 \\ \hline
      ml\_stripped & 736 & 344 & 843 & 237 & 283 & 797 & 1862 & 1378 \\ \hline
      ml & 866 & 214 & 876 & 204 & 257 & 823 & 1999 & 1241 \\ \hline 
      ml\_enriched & 881 & 119 & 797 & 283 & 284 & 798 & 1962 & 1278 \\ \hline
      ml\_advanced  & 856 & 224 & 808 & 272 & 292 & 788 & 1956 & 1284 \\ \hline
      ml\_combined & 949 & 131 & 759 & 321 & 274 & 806  & 1982 & 1258\\ \hline
  \end{tabular}
\end{center}
\textbf{Table 1}: Overview of tournament wins and losses per ml-bot. \\

\begin{center}
\begin{tabular}{| r | r | r | r || r |}
\hline
      & \textbf{rand} & \textbf{bully} & \textbf{rdeep} & \textbf{Total} \\ \hline
      ml\_minimal & -2,65\% & -4,45\% & +35,4\% & \textbf{+1,45\%}   \\ \hline
      ml\_stripped & -15\% & -3,76\% & +10,11\% & \textbf{-6,85\%}  \\ \hline
      ml\_enriched & +1,73\% & -9,01\% & +10,5\% & \textbf{-1,85\%} \\ \hline
      ml\_advanced & -1,15\% & -7,76\% & +13,6\%& \textbf{-2,15\%}  \\ \hline
      ml\_combined & +9,58\% & -13,35\% & +6,61\% & \textbf{-0,85\%}  \\ \hline \hline
      Average improvement & \textbf{-1,5\%} & \textbf{-7,67\%} & \textbf{+15,24\%} &\textbf{-2,05\%} \\ \hline
\end{tabular} \\
\end{center}

@@

\begin{center}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotRand.png}
\captionof{figure}{Part of games won against Rand}
\end{minipage}
\hfill
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotBully.png}
\captionof{figure}{Part of games won against Bully}
\end{minipage}
      \\ %extra line for space
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth]{images/barplotRdeep.png}
\captionof{figure}{Part of games won against Rdeep (notice the Y-axis)}
\end{minipage}
\end{center}

\section{Findings}
From the collected data we have x conclusions.

\subsection*{Against Rand}

\subsection*{Against Bully}

\subsection*{Against Rdeep}
First of all, the learning bots performed worse than rdeep.The worst performer was, surprisingly, the stock ml bot. The performance of each bot
